Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
section

\begin{proof}
We reformulate $t$-liveness 
in a 
reset-VASS $(Q,T)$ 
with initial configuration $s_0$
as the following formula
\[ ~ \forall p(\textbf{u}) \in Q \times \N^d, 
~ s_0 \rightarrow^* p(\textbf{u}) \implies \exists q(\textbf{v}) \in pre(t), ~ p(\textbf{u}) \rightarrow^{*} q(\textbf{v})\]  
The problem reduces itself to {\sc State-resilience}
where $\Safe = pre(t)$.
\end{proof}

The following theorem is a transposition of Theorem~5.5 from \cite{peterson1981petri} from Petri nets to reset-VASS, whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to {\sc $t$-liveness}.
\end{proposition}

>>>>

\begin{proof}
We reformulate $t$-liveness 
in a 
reset-VASS $(Q,T)$ 
with initial configuration $s_0$
as the following formula
\[ ~ \forall p(\textbf{u}) \in Q \times \N^d, 
~ s_0 \rightarrow^* p(\textbf{u}) \implies \exists q(\textbf{v}) \in pre(t), ~ p(\textbf{u}) \rightarrow^{*} q(\textbf{v})\]  
The previous formula reduces itself to {\sc State-resilience}
where $\Safe = pre(t)$.
\end{proof}

The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets, whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to {\sc $t$-liveness}.
\end{proposition}
